Code walkthrough

### 2022-11-02 src/explore_aghq/aghq.Rmd
Add pdf output of AGHQ examples

```{r}
plot <- data.frame(x = seq(from = -10, to = 10, by = 0.1)) %>%
  mutate(
    y = f(x)
  ) %>%
  ggplot(aes(x = x, y = y)) +
    geom_line() +
    labs(x = "x", y = "f(x)") +
    theme_minimal()

@@

plot +
  geom_point(
    data = data.frame(nodes = gg$nodes, weights = gg$weights, y = 0), 
    aes(x = nodes, y = y, size = weights),
    col = cbpalette[2]
  ) +
  scale_size_continuous(limits = c(1, 2))
```

@@

plot2 <- df %>%
  rowwise() %>%
  mutate(
    y = f(c(x1, x2))
  ) %>%
  ggplot(aes(x = x1, y = x2, fill = y)) +
    geom_tile() +
    theme_minimal()

@@

```{r}
plot2 +
  geom_point(
    data = mvQuad::getNodes(gg2) %>%
            as.data.frame() %>%
            mutate(weights = mvQuad::getWeights(gg2)), 
    aes(x = V1, y = V2, size = weights, fill = 1),
    col = cbpalette[2]
  ) +
  labs(col = "f(x1, x2)") +
  scale_size_continuous(limits = c(2, 4))
```

>>>>

```{r}
plot <- data.frame(x = seq(from = -10, to = 10, by = 0.1)) %>%
  mutate(
    y = f(x)
  ) %>%
  ggplot(aes(x = x, y = y)) +
    geom_line(col = cbpalette[1]) +
    labs(x = "x", y = "f(x)") +
    theme_minimal()

@@

plot <- plot +
  geom_point(
    data = data.frame(nodes = gg$nodes, weights = gg$weights, y = 0), 
    aes(x = nodes, y = y, size = weights), alpha = 0.5
  ) +
  labs(size = "Weight") +
  scale_size_continuous(limits = c(1, 2))

plot

ggsave(filename = "aghq-1d.pdf", plot = plot, height = 4, width = 6.25)
```

@@

plot2 <- df %>%
  rowwise() %>%
  mutate(
    y = f(c(x1, x2))
  ) %>%
  ggplot() +
    geom_contour(aes(x = x1, y = x2, z = y), col = multi.utils::cbpalette()[1]) +
    theme_minimal()

@@

```{r}
plot2 <- plot2 +
  geom_point(
    data = mvQuad::getNodes(gg2) %>%
            as.data.frame() %>%
            mutate(weights = mvQuad::getWeights(gg2)), 
    aes(x = V1, y = V2, size = weights),
    alpha = 0.5
  ) +
  labs(col = "f(x1, x2)", size = "Weight") +
  scale_size_continuous(limits = c(2, 4))

plot2

ggsave(filename = "aghq-2d.pdf", plot = plot, height = 4, width = 6.25)
```

### 2022-11-02 src/explore_aghq/walkthrough.Rmd
Add pdf output of AGHQ examples

pdfandcdf <- compute_pdf_and_cdf(quad$marginals[[i]], interpolation = interpolation)

@@

```{r}
for (i in 1:length(q)) out[i] <- pdfandcdf$theta[max(which(pdfandcdf$cdf < q[i]))]

>>>>

pdf_and_cdf <- compute_pdf_and_cdf(quad$marginals[[i]], interpolation = interpolation)

@@

```{r}
for (i in 1:length(q)) out[i] <- pdf_and_cdf$theta[max(which(pdf_and_cdf$cdf < q[i]))]
